Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-06-06 composition.tex
fixed comments by Naeem

Selection and declustering was also done in consistence with the original catalog, using the methods by \citet{Gardner1974}, \citet{Reasenberg1985} and \citet{Uhrhammer_1986_EN}. We obtained the declustered version of \citet{Zare2014}, selected 7,478 earthquakes within our region of interest, and removed 605 foreshocks and 2,917 aftershocks, leaving only those events in agreement with a Poissonian model. The same procedure was used for the added events between 2000 and 2015. These steps altogether allowed us to preserve compatibility with the original catalog while also including the most recent events. The final set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.

>>>>

Selection and declustering was also done in consistence with the original catalog, using the method of \citet{Gardner1974}. In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events prior to 2000, complemented with all $M>3$ events from 2000 to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks. The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.

### 2016-06-06 hazard.tex
re-organized titles and files
fixed comments by Naeem

\section{Approach to Seismic Hazard}

@@

In this study we use the smoothed seismicity method introduced by \citet{Frankel1995}. This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}. In it, the $b$-value is usually assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes. The spatial variation of $a$ is defined based on dividing the region of interest into regular-size grid cells. The parameter $a$ is determined based on the number of events $n_i$ within each cell $i$ of magnitude greater than a reference value $M_{\mathrm{ref}}$, and discretized in different magnitude ranges (or bins). The number of earthquakes within each cell is then smoothed spatially taking into account the values of neighboring cells using a Gaussian function. In essence, the smoothed seismicity approach addresses the aleatoric uncertainty of future earthquake locations by using a weighted contribution of the background regional seismicity, and thus eliminates the need for knowledge about specific fault locations.

@@

In turn, we consider the $b$-values to be constant within each seismic zone as delimited in Fig.~\ref{fig:iran}. Details about the calculation of the $b$-value for each zone are provided below. By contrast, in the recent work by \citet{Khodaverdian_2016_BSSA}, the authors computed spatially-variable $b$-values within super-grid cells of size 1\textdegree{} $\times$ 1\textdegree{} and $a$-values within the usual grid cells of size 0.1\textdegree{} $\times$ 0.1\textdegree{}. While this approach is novel in the sense that it also grids $b$-values, these super-cells may easily cross over zones of different seismogenic characteristics, and thus may not be faithful to the nature of earthquakes within any given zone. Admittedly, these are subjective decisions and any reasonable choice may be valid and within the margins of the associated epistemic uncertainty.

>>>>

\section{Seismic Hazard Approach}

@@

In this study we use the smoothed seismicity method introduced by \citet{Frankel1995}. This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}. In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes. The spatial variation of $a$ is defined based on dividing the region of interest into regular-size grid cells. The parameter $a$ is determined based on the number of events $n_i$ within each cell $i$ of magnitude greater than a reference value $M_{\mathrm{ref}}$, and discretized in different magnitude ranges (or bins). The number of earthquakes within each cell is then smoothed spatially taking into account the values of neighboring cells using a Gaussian function. In essence, the smoothed seismicity approach addresses the aleatoric uncertainty of future earthquake locations by using a weighted contribution of the background regional seismicity, and thus eliminates the need for knowledge about specific fault locations.

@@

In turn, we consider the $b$-values to be constant within each seismic zone as delimited in Fig.~\ref{fig:iran}. Details about the calculation of the $b$-value for each zone are provided below. By contrast, in the recent work by \citet{Khodaverdian_2016_BSSA}, the authors computed spatially-variable $b$-values within large grid-cells of size 1\textdegree{} $\times$ 1\textdegree{} based on the average seismicity within a 200-km radius from each cell. While gridding $b$-values and considering the influence of neighboring large-size cells allows to draw information from the background seismicity, it is unavoidable to have the contributing areas cross over seismic zones of different characteristics, which may pollute the computation of $b$-values. Admittedly, these are subjective decisions and any reasonable choice can be considered valid or within the margins of the associated epistemic uncertainty.
